---
title: "Camping Weather notebook"
output: html_notebook
---

Notes and testing for the Camping Weather shiny app.

Doug Merrett ⓒ 2022 OFH Consulting

```{r}
## Install the required package with:
## install.packages("RSocrata")

library("RSocrata")
library("dplyr")
library("lubridate")
```
### Load JSON data from the socrata API endpoint.
Definitely need to pare the load down, even pulling one stations grabs over 100,000 records
Should only need 4 days worth over however many years available
```{r}
startTime <- Sys.time()

df <- read.socrata(
  "https://data.novascotia.ca/resource/kafq-j9u4.json?$select=site_id,datetimeutc,air_temperature,date_extract_m(datetimeutc) as month&$where=month = 10 AND site_id='RNSGV'",
  app_token = "YIJmci7v0Fd0eHtco6IXgFBuP"
)
endTime <- Sys.time()
  
# prints recorded time
print(endTime - startTime)
```
### After the site load dig in to the data.

```{r}
unique(year(df$datetimeutc))
```

Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Ctrl+Alt+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Ctrl+Shift+K* to preview the HTML file).

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.
